The Impact of the 2022-23 NBA Rule Change

### 2024-04-25 paper/paper.qmd
Update introduction section
Update key findings

A clear gap exists in understanding the nuanced impacts of the new transitional foul rule on player performance and MVP considerations, especially when compared to the previous season. This paper seeks to fill this gap by thoroughly analyzing the statistical data from both the 2022-23 and 2021-22 NBA seasons to highlight the changes, continuities, and emerging trends over these times. To address this gap, we used the R programming language [@citeR] to analyze shooting performance metrics, such as field goal percentage (FG%), three-point percentage (3P%), free throw percentage (FT%), as well as MVP voting points won from both seasons. Our findings reveal no statistically significant relationships between shooting efficiency and MVP points in the 2022-23 NBA season.

>>>>

A clear gap exists in understanding the nuanced impacts of the new transitional foul rule on player performance and MVP considerations, especially when compared to the previous season. This paper seeks to fill this gap by thoroughly analyzing the statistical data from both the 2022-23 and 2021-22 NBA seasons to highlight the changes, continuities, and emerging trends over these times. To address this gap, we used the R programming language [@citeR] to analyze shooting performance metrics, such as field goal percentage (FG%), three-point percentage (3P%), free throw percentage (FT%), as well as MVP voting points won from both seasons.

Our results in FG% showed a positive but statistically insignificant relationship with MVP points. 3P% had a negative relationship with MVP points, also statistically insignificant. FT% showed a positive but statistically insignificant relationship with MVP points. The model had a high residual standard error (314.30), indicating substantial unexplained variability, and a low Adjusted R-squared (0.17), suggesting potential overfitting or irrelevance of some variables. Therefore, our findings reveal no statistically significant relationships between shooting efficiency and MVP points in the 2022-23 NBA season.
